Dynamic Prediction of Non-Guassian Outcome with fast Generalized Functional Principal Analysis

### 2023-03-07 Write-ups/Manuscript.Rmd
manuscript outline

Method
=================================================================================================================================
-	Need better notation system

Result
=================================================================================================================================
-	Repeat simulation: is it necessary in this case?
-	Different set-up:
a.	Different eigenfunctions: with or without periodicity
b.	Outcome: binary or count
c.	Sample size
d.	Grid density
e.	Bin width, overlap or not
-	Real data application

>>>>

Method
=================================================================================================================================

-	Need better notation system
- Change to general exponential family
- Add section of de-bias score: conditional on subject. Need repeat simulation to demonstrate

Result
=================================================================================================================================
-	Repeat simulation: repeat 10-100 times

-	Different set-up:
a.	Different eigenfunctions: with or without periodicity (start with the current one)
b.	Outcome: binary or count
c.	Sample size: start with N=500
d.	Grid density: start with J=1000
e.	Bin width, overlap or not: start with non-overlap, bin width = 10 (100 bins)

-	Real data application

### 2023-03-07 Write-ups/Manuscript.tex
manuscript outline

\begin{itemize}
\tightlist
\item
  Need better notation system
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Repeat simulation: is it necessary in this case?
\item
  Different set-up:
\end{itemize}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Different eigenfunctions: with or without periodicity
\item
  Outcome: binary or count
\item
  Sample size
\item
  Grid density
\item
  Bin width, overlap or not
\end{enumerate}

>>>>

\begin{itemize}
\tightlist
\item
  Need better notation system
\item
  Change to general exponential family
\item
  Add section of de-bias score: conditional on subject. Need repeat
  simulation to demonstrate
\end{itemize}

@@

\begin{itemize}
\item
  Repeat simulation: repeat 10-100 times
\item
  Different set-up:
\end{itemize}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Different eigenfunctions: with or without periodicity (start with the
  current one)
\item
  Outcome: binary or count
\item
  Sample size: start with N=500
\item
  Grid density: start with J=1000
\item
  Bin width, overlap or not: start with non-overlap, bin width = 10 (100
  bins)
\end{enumerate}
